Title

### 2023-10-21 Response to Reviewers.tex

\documentclass[10pt,letterpaper]{article} % {{{
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
\usepackage{amsmath,amssymb}
% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% textcomp cpackage and marvosym package for additional characters
\usepackage{textcomp,marvosym}
\usepackage{subcaption}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage[nopatch=eqnum]{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% color can be used to apply background shading to table cells only
\usepackage[table]{xcolor}

% array package and thick rules for tables
\usepackage{array}
\usepackage{caption}
\captionsetup[figure]{labelfont={bf},labelformat={default},labelsep=period,name={Fig}}

% create "+" rule type for thick vertical lines
\newcolumntype{+}{!{\vrule width 2pt}}

% create \thickcline for thick horizontal lines of variable length
\newlength\savedwidth
\newcommand\thickcline[1]{%
  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
  \cline{#1}%
  \noalign{\vskip\arrayrulewidth}%
  \noalign{\global\arrayrulewidth\savedwidth}%
}

% \thickhline command for thick horizontal lines that span the table
\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
\hline
\noalign{\global\arrayrulewidth\savedwidth}}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\renewcommand{\figurename}{Fig}
\renewcommand{\succ}{\textrm{succ}}

\newcommand{\fref}[1]{Fig~\ref{#1}}
\newcommand{\eref}[1]{Eq~(\ref{#1})}
% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}

\usepackage[english]{babel}
\usepackage{graphicx,helvet}
\usepackage{color}
\usepackage{url}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
% \usepackage[inline]{showlabels}
\usepackage{bbm,bm}
\usepackage{soul}
\usepackage{amsfonts}

\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{quantikz}

\usepackage[draft,inline,nomargin]{fixme} \fxsetup{theme=color}
\FXRegisterAuthor{cp}{acp}{\color{blue}CP}
\FXRegisterAuthor{tb}{ttb}{\color{green}TB}

%\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
%\setlength{\headheight}{27.023pt}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\today}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}
\DeclareMathOperator{\tr}{tr}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}

%% END MACROS SECTION

% }}}
\begin{document}

\section{Response to Editor:}

We are re-submitting our paper ``Quantum simulation of Pauli channels and dynamical maps: algorithm and implementation''. 
We believe that the revised version of our paper addresses all
concerns by the referees in detail and is suitable for publication.

\section*{Reviewers' General Comments}

\textbf{Reviewer 1:} \\

\textbf{
The paper presents two results: 1. A way to simulate
parametric Pauli Channels using a gate-based formalism, useful for
quantum computation, and 2. An investigation on the class of
parametric Pauli Channels that can be parametrised by acting only on
one qubit via one parameter.
The full detailed comments on the paper are attached in the pdf file.
My general comments are the following:
\begin{itemize}
\item[1.]The two aforementioned results are disjointed and completely
lacking in motivation. The entire logic of the paper is obscure, and
seemingly lacks any ground for the results to be useful in any way.
\item[2.] The simulation on the IBM quantum computer is irrelevant, and does
not prove neither the validity of the decomposition (as it fails for
most of the range of operations) nor it is quantifiying any relevant
parameter (noise for example). Data from those experimental runs and
complete methodology for calculating the diamond norm is also missing.
\item[3.] The claims are vague, and the mathematical formalism is vague, with
strong abuse of notation and non-strict definitions and theorems.
There are also many spelling mistakes and refuses, even in the
formulas.
\item[4.] The analysis on the 1-parametrisation is lacking a discussion on
what happens at higher than 2 dimensions.
\end{itemize}
For the aformenetioned reasons, I cannot reccomend this paper for
publication. I suggest the following three course of actions:
\begin{itemize}
\item[1.] Separate the two main results.
\item[2.]Improve the tightness of the mathematical formalism.
\item[3.]  Find an application of the generalised Pauli Channels that can be
effectively simulated with the methodology.
\end{itemize}
}

\textbf{Reviewer 2:} \\
\textbf{The authors introduced some quantum circuits to implement the action
of arbitrary Pauli channels using fixed-state ancilla qubits, and
certain single-parameter Pauli dynamical channels using
one-parameter-rotation circuits consisting of one parametrized
single-qubit rotation and two unparametrized multiqubit unitary
operations. They showed that the latter class of dynamical channels
implementable is related to the one-parameter ancilla-state curves
allowable for such circuits. This is understandable since only a
single-parameter controlled rotation is used for the circuit, which
does not offer sufficient flexibility to realize all single-parameter
Pauli dynamical channels from my understanding.}

\textbf{While the implementations appear to be mathematically sound, there
appears to be a lack of comparisons between the actual channel
implemented and the target channel. There is only one Fig. 3 that
shows the diamond fidelities for homogenously-chosen single-qubit
unparametrized Pauli target channels within the tetrahedron region.
This is a nice plot that reveals the realistic errors coming from the
IBM quantum cloud, namely that the single-qubit Pauli channels
corresponding to the central part, which I presume are the
depolarizing channels, have the highest diamond fidelity.}

\textbf{
Besides this plot, the authors however did not show the performance of
their algorithms for larger number of qubits, and there are no
performance plots for dynamical Pauli-channel implementations. For a
further evaluation as to whether the algorithms are scientifically
practical, at least a plot on two-qubit Pauli channels and one on
two-qubit dynamical Pauli channels. My take is that because the
unitary operators A and B are too sophisticated for hardware
implementations, since they are even more complicated than single
controlled unitary operators, the fidelity could be very strongly
peaked around the zero of the pseudo Bloch-vector space for multiqubit
systems. If the overall system is too large even for simulating
two-qubit channels (due to the ancillas), then classical numerical
simulations are sufficient.}

\textbf{
In any case, after supplying the performance plots, I believe that the
algorithms and performance plots shall supply a fair presentation on
the scientific soundness of this work.}

\section{Comments throughout the text}

\begin{enumerate}
\item \textbf{I fail to see the point here, the logic of the paper is: 
1. ``open quantum systems can be modeled through a class of channels representing he various types of decoherence.'' 2. ``Quantum circuits are a convenient gate-based formalism that is well understood and has an extensive body of work, and experimentally accessible.''
3. We map (generalised) Pauli channels onto quantum circuits, as a way to simulate them.}

\textbf{What I am missing is what do we learn by doing it which cant be learned by actually performing the Pauli channel onto a quantum system? For example, applying well controlled sx, sy, sz operations and their coherent parametric combination using a photonic polarisation or path encoding is experimentally trivial. Why would I need to decompose (not even effectively for any channel) the pauli channels to match a gate based description? Which class of problems can we simulate that cannot be simulated otherwise? Is there any advantage (for example in speed up, resources like ancillas required, resistance to unwanted noise etc..?)}

\textbf{Intuitively, it seems incredibly harder resource wise to create the sum b|gamma> superposition state needed for the ancilla, just for the sake of having it into a "quantum circuit" perspective.}\\

\item \textbf{ Really confusing notation, I suggest use the much more well known relation using the Levi-Civita tensor.}\\

A sentence was added to the text mentioning how we get to the equation by starting with the relation $[\sigma_\alpha,\sigma_\beta] = 2 i
\epsilon_{\alpha \beta \gamma} \sigma_\gamma$.
After using this equation on $\sigma_{\alpha} \sigma_{\gamma} \sigma_{\alpha}$, the Levi-Civita are summed out and we are left with:
\begin{equation*}
\sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma}  =   A_{\alpha,\gamma} \sigma_{\alpha}, \;\;\;\;\;\; \text{with} \; A_{\alpha, \gamma} = (2\delta_{\alpha \gamma}-1)(2\delta_{\alpha 0}-1)(2\delta_{\gamma 0}-1)
\end{equation*}
We believe that writing matrix $A$ explicitly is more simple than this expression.

\item \textbf{Eq 2} \\

The correct equation is indeed equation 1, since we are referring to the fact that 
\begin{equation}
\label{eq: rho-transformada}
\mathcal{E}(\rho) = \dfrac{1}{2} \sum_{\alpha} \left(\sum_{\gamma} A_{\alpha, \gamma} k_{\gamma} \right) r_{\alpha} \sigma_{\alpha}.
\end{equation}
has the form of $\dfrac{1}{2} \sum_{\alpha} r_{\alpha} \sigma_{\alpha}$, only with the
$r_{\alpha}$ replaced by $\left( \sum_{\gamma} A_{\alpha,\gamma} k_{\gamma} \right) r_{\alpha}$.

\item \textbf{ At this point I am missing a proper defiition of a "quantum circuit" consistent with the mathematical formalism. The authors start from the very basic regarding Pauli channels, but give for granted the quantum circuit formalism.} \\

We added a few lines at the beginning of section 3 defining the concept of quantum circuit.
We  mention that quantum circuits are a representation of computation on quantum systems, which applies a unitary operator $U$ on it.

\item  \textbf{So another way to see this is that the simulation through the proposed decomposition works only for depolarising channels, and fails otherwise.}\\

The algorithm works to some extent for all Pauli channels, and how well
it does or does not work is quantified by the fidelity.
Indeed, the result we got is that it works much better for channels that are depolarizing
and works less well as we get closer to unitary channels.

\item \textbf{Why?}\\
We rephrased the sentence to make the point more clear
and explained that as a consequence of the circuit being usable in general for any Pauli channel,
it implements unitary channels in a very roundabout way.

\item \textbf{I wholeheartedly agree with this statement, and I would go so far as to claim that this is true in general, even at the center of the tethraedron.} \\

\item \textbf{but this is a severe disadvantage, that begs the question: what is the advantage?} \\

The advantages are that it is a straightforward, concrete and general way
of simulating Pauli channels.
Being general gives the possibility to later use it for Pauli dynamical maps by only needing to vary a few parameters.

\item \textbf{This definition is vague - given the vagueness of the term "quantum circuit".
 Here what you are defining is just a unitary operation acting on a N-qubit Hilbert space, that is parameter dependent only locally on one specific qubit. } \\

We added a sentence explaining that to make it more concrete.

\item \textbf{Normal}\\

They are only orthogonal, since their individual norms are not equal to $1$.

\item \textbf{Again, this is not a conclusion from theorem 1. This is literally Definition 1. Also, use the proper notation here - make A and B operators living on an dim N Hilbert state, and R explixitly dependent on s and operating on qubit N. Then the matrix representation of the operators is a $2^n\times 2^n$ matrix which is applied to the state j. The explanation in words in not sufficient.} \\

We rephrased the first paragraph of the proof to make it more clear when we use the result of theorem 1. 
Basically, we first use definition 1 to say that the circuit has the form $ARB$,
and then the result of theorem $1$
to conclude that $R$ is actually a $\sigma_3$ rotation
of angle $2s$ applied to the last qubit.\\

\item \textbf{true only if the initial j states are normalised, but they were undefined.}\\

We added the definition of $|j\rangle$  at the end of the theorem statement.\\

\item \textbf{How can it make sense to define A and B applied respectively to the last 3 and the first qubit?}\\

We changed the phrasing to make it more clear that $A$ and $B$ 
are restricted to act in a particular way on the last 3 and first qubit respectively.
Besides from that, the remaining parts of the operators $A$ and $B$ can be chosen arbitrarily, 
with the only restriction that the resulting matrices are unitary. \\

\item  \textbf{Please, at least give an example of this semiarbitrary construction of A and B.}\\

We added examples of these matrices for three particular dynamical maps in the next section. \\

\item \textbf{I don't understand what operatively is happening here. Select the state 0, apply B, apply $R_s$, apply A and then "straight forward calculations" lead to what?} \\

We rephrased this part to make it clearer. The idea is that we are searching for the matrices $A$ and $B$ such
that for given vectors $|a\rangle, |b\rangle, |c\rangle$, the circuit creates
the state $e^{is(p)} |a \rangle + e^{-is(p)} |b \rangle + |c\rangle$.
In this part, we show that with the matrices $A$ and $B$ we constructed,
we indeed create said state.
That way, given any curve of states that can be done with a 1PR circuit
according to theorem 2, here we show how
to actually create said circuit (that is, which matrices $A$, $B$ to select).\\

\item \textbf{To see what?} \\

As said before, to see that the selection of matrices $A$, $B$ creates 
the curve of states we wanted.
This part of the text has been rewritten to make it clearer.\\

\item \textbf{so this is just the proof that the proposed operative definition of A and B is properly normalised, right?} \\

This is an intermediate step, but as said in the previous questions, 
we are proving that the selection of $A$ and $B$ for given vectors $|a\rangle, |b\rangle, |c\rangle$ 
indeed works to create the state
$e^{is(p)} |a \rangle + e^{-is(p)} |b \rangle + |c\rangle$.\\

\item \textbf{To be consistent with the previous formalism, the states should be 0,1,2,3}\\

We made the change.\\

\item \textbf{there is literally one parameter in one qubit, of course it depends on one parameter...
 how can this be a result?} \\

The result is that they needed  to move just one parameter to implement 
many Pauli channels in the bit flip maps.
For other maps, they may need to move more than one parameter to 
implement all the channels in the map. 
However, just as we showed that the bit flip map can be done with a 1PR circuit,
they implemented the map using one parameter.\\

 \item  \textbf{This is interesting, instead of giving only some random examples, I would actually explore more in details the zoology of this class of dynamical maps - if lucky, you would find class of interesting problems that can be simulated effectively in an experimental setup by just accessing one parameter (as the authors say, just with one set of waveplates, for example)} \\

Some of the examples given (depolarizing, bit flip, phase flip, bit-phase flip) are very well known 
Pauli maps.
We also included random examples with the purpose of seeing how some general maps that 
can be implemented with a 1PR circuit look like.

 \item  \textbf{I feel that there needs to be a treatment of what happens, at least qualitatively at higher than two dimension, as one of the selling point is the generality of the formalism for N qubit. I expect, however, that the higher the dimension, the less rich is the space that can be parametrised by only one parameter, so.. what is the applicability of the theorem for higher dimensions?} \\

 We added a couple of sentences talking about that.

 \item \textbf{Imprcise} \\

 We

 \item This reasoning I miss, simplifying for achieving what goal?

 \item There is no quantification of this, it´s not even the focus of the paper

 \item citation required here
\end{enumerate}

\end{document}

### 2023-10-21 main.tex
Algunos cambios

\tbnote{Propuesta haciendo unos cambios de enfoque que menciono en la intro:}\\
$\;$ \\

{\color{green}
Pauli channels are fundamental in the context of quantum computing as they
model the simplest kind of noise in quantum devices, and
Pauli dynamical maps are parametrized Pauli channels,
which can model a continuous transformation of a quantum device.
In this article, we propose a quantum
algorithm for simulating
Pauli dynamical maps
by using a parametrized quantum circuit.
We also establish the mathematical conditions for an
$N$-qubit transformation to be achievable using a parametrized circuit where
only one single-qubit operation depends on the parameter. 
The implementation of the proposed circuit is demonstrated using IBM's quantum computers 
for the case of one qubit, and the fidelity of this implementation is reported. 
}
% }}}
\section{Introduction} % {{{

@@

Since their inception, quantum computers were proposed as powerful tools for
the simulation of quantum systems~\cite{feynman1982simulating}.  Being open
quantum systems of fundamental~\cite{Zur91,RevModPhys.76.1267} and
practical~\cite{breuer2007theory} interest, there has been efforts towards the
simulation of the evolution of open quantum systems~\cite{Garcia, Wang,Weimer}
and specifically for quantum channels~\cite{Xin,Wei,Zanetti}.
Such quantum algorithms can be represented using what is known as a quantum
circuit~\cite{chuangbook}, which we will study in section \ref{sec: Circuit for a Pauli Channel}.

@@

To represent the algorithms implemented in quantum computers, either to
simulate a physical system or for some other purpose, one often uses a quantum
circuit~\cite{chuangbook}.  In this work, we shall also work with parametrized
quantum circuits, that is,  quantum circuits in which some of the operations
depend on variable parameters~\cite{cerezo}.  These circuits play an important
part in applications such as quantum machine learning~\cite{Benedetti} and
describing general quantum transformations dependent on parameters. Substantial
research has been devoted to enhancing the efficiency of these
circuits~\cite{Rasmussen}.

@@

\cpnote{dejar solo un parrafo de estructura}
We start by providing the definition of quantum channels, the general framework
used here, and multi-qubit Pauli channels in section \ref{sec: Pauli Channels}.
Our first objective is to present a quantum algorithm capable of simulating
Pauli channels on quantum computers; we do this in section \ref{sec: Circuit
for a Pauli Channel}, where we also demonstrate its implementation using IBM's
quantum computers for the particular case of single-qubit Pauli channels.
Expanding beyond discrete Pauli channels, we introduce the concept of Pauli
dynamical maps, defined as a continuous parametrization of multi-qubit Pauli
channels.  Therefore, in section \ref{sec: 1PR Circuits} we shift our focus to
study parametrized quantum channels, aiming to adapt the algorithm developed
for channels to dynamical maps.  Furthermore, we contribute to the body of work
related to parametrized quantum circuits by establishing a theorem, which  sets
the mathematical conditions for the transformations that can be done using a
parametrized circuit with the restriction that only a controlled single-qubit
rotation in the circuit may depend on the parameter.  Finally, in section
\ref{sec: 1PR circuit for a Pauli map}, we conclude analyzing the Pauli
dynamical maps that fulfill the conditions of theorem \ref{theorem2}.

We start the article by providing the definition of quantum channels, the
general framework used here, and multi-qubit Pauli channels in section
\ref{sec: Pauli Channels}.  Then, since our main objective is to obtain a
parametrized circuit for Pauli dynamical maps, we will first need a circuit
that can implement any Pauli channel by only changing some parameters in the
quantum gates and without changing the design of the circuit itself.
Therefore, in section\ref{sec: Circuit for a Pauli Channel} we present such a
circuit and we also show its implementation using IBM's quantum computers for
the particular case of single-qubit Pauli channels and some two-qubit ones.  In
section \ref{sec: 1PR Circuits}, we adapt the algorithm to dynamical maps.
Then we aim to simplify the algorithm so that it only contains one parametrized
single-qubit rotation, and in the process we contribute to the work in
parametrized quantum circuits by establishing   in \ref{theorem2} which general
quantum transformations can be implemented this way.  Finally, in section
\ref{sec: 1PR circuit for a Pauli map}, we conclude analyzing the Pauli
dynamical maps that fulfill the conditions of theorem \ref{theorem2}.

@@

We can also see how an arbitrary Pauli channel acts on an arbitrary  
density matrix.
To do it, we substitute \eref{eq: Density Matrix} 
in \eref{eq: Pauli channel 1 qbit}:
\begin{equation}
\mathcal{E}(\rho) = \dfrac{1}{2}\sum_{\gamma,\alpha=0}^3 k_{\gamma} r_{\alpha} \sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma}.
\label{eq:Edepol}
\end{equation}
This can be simplified noting that 
\begin{equation}
\sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma} = A_{\alpha,\gamma} \sigma_{\alpha}, \;\;\;\;\; \text{with} \; A = \begin{pmatrix}
1 & 1 & 1 & 1\\
1 & 1 & -1 &-1 \\
1 & -1 & 1 & -1 \\
1 & -1 & -1 & 1
\end{pmatrix},
\end{equation}
which was obtained following the 
commutation relation of Pauli matrices $[\sigma_\alpha,\sigma_\beta] = 2 i
\epsilon_{\alpha \beta \gamma} \sigma_\gamma$ and $\epsilon_{\alpha \beta \gamma}$ is 
the Levi-Civita tensor. Then, \eref{eq:Edepol} takes the form
% 
% 
% 
% 
% This can be simplified by using the following property of Pauli matrices:
% \revnote{Really confusing notation, I suggest use the much more well known relation using the Levi-Civita tensor.}
% 
% 
% \tbnote{Siguiendo la relaci\'on de conmutaci\'on, resulta que las Levi Civitas desaparecen y quedan s\'olo deltas de Dirac:}
% {\color{green}
% \begin{equation*}
% \sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma}  =   A_{\alpha,\gamma} \sigma_{\alpha}, \;\;\;\;\;\; \text{with} \; A_{\alpha, \gamma} = (2\delta_{ij}-1)(2\delta_{i0}-1)(2\delta_{j0}-1)
% \end{equation*}
% }
% 
% 
% \begin{equation}
% \label{eq: propiedad-pauli}
% \sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma} = A_{\alpha,\gamma} \sigma_{\alpha}, \;\;\;\;\; \text{with} \; A = \begin{pmatrix}
% 1 & 1 & 1 & 1\\
% 1 & 1 & -1 &-1 \\
% 1 & -1 & 1 & -1 \\
% 1 & -1 & -1 & 1
% \end{pmatrix},
% \end{equation}
% which leads to
\begin{equation}
\label{eq: rho-transformada}
\mathcal{E}(\rho) = \dfrac{1}{2} \sum_{\alpha} \left(\sum_{\gamma} A_{\alpha, \gamma} k_{\gamma} \right) r_{\alpha} \sigma_{\alpha}.
\end{equation}
\eref{eq: rho-transformada} once again has the form of \eref{eq: Density Matrix}
but with components $\left( \sum_{\gamma} A_{\alpha,\gamma} k_{\gamma} \right) r_{\alpha}$.
This gives us another way of understanding Pauli channels
as operations that take each component $r_{\alpha}$
of the density matrix and multiplies them
by $\sum_{\gamma} A_{\alpha,\gamma} k_{\gamma}$, 
that is:
\begin{equation}
\label{eq: multipliers}
r_{\alpha}  \xrightarrow[\text{Channel}]{\text{Pauli}}  \tau_{\alpha} r_{\alpha} ,\;\; \tau_{\alpha} := \sum_{\gamma} A_{\alpha,\gamma} k_{\gamma}.
\end{equation}
Notice that $\tau_0 = 1$, which is a consequence of $\sum_{\gamma}k_{\gamma}=1$
and ensures that after the channel, the resulting density matrix still has trace one. 
Furthermore, reverting the definition of $\tau_{\alpha}$ by using that $A^{-1} = \dfrac{1}{4} A$, 
we get that $k_{\gamma} = \dfrac{1}{4} \sum_{\alpha} A_{\alpha,\gamma} \tau_{\alpha}$.
Then, using that $k_{\gamma} \geq 0$
we get the following conditions on the multipliers $\tau_{\alpha}$:
\begin{eqnarray}
\label{eq: conditions-tetrahedron}
&1+\tau_i -\tau_j - \tau_k \geq 0,  \;\;\; \text{for $i,j,k$ different numbers in $\{1,2,3\}$}, \\
&1+\tau_1 + \tau_2 + \tau_3 \geq 0.
\end{eqnarray}

@@

{\color{green}
\subsection{Simulation of a two-qubit Pauli channel}
\tbnote{Voy a agregar toda esta sección sobre el circuito para dos qubits}

For the case of a two-qubit Pauli channel,
the circuit of \fref{Fig1} would have two main
qubits and four ancilla qubits, on which it would be necessary to create the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma}\rangle$.
However, the number of ancilla qubits can be reduced for Pauli 
channels in which not all two-qubit Pauli matrices are applied to
the system. For example, consider the following two-qubit dephasing channel:
\begin{align}
\varepsilon (\rho) = (1-p) \rho + \dfrac{p}{3} (I \otimes \sigma_z) \rho (I \otimes \sigma_z) +  \dfrac{p}{3}(\sigma_z \otimes I) \rho (\sigma_z \otimes I) +  \dfrac{p}{3}(\sigma_z \otimes \sigma_z) \rho (\sigma_z \otimes \sigma_z),
\label{2qbit-c}
\end{align}
where $p \in [0,1]$ is a parameter that defines the channel. 
Since this channel has $4$ Pauli operations, 
only $2$ ancilla qubits will be necessary, and it can be implemented
using the circuit of \fref{2qbit}a).

>>>>

% }}}
\section{Introduction} % {{{

@@

Since their inception, quantum computers were proposed as powerful tools for
the simulation of quantum systems~\cite{feynman1982simulating}.  Being open
quantum systems of fundamental~\cite{Zur91,RevModPhys.76.1267} and
practical~\cite{breuer2007theory} interest, there has been efforts towards the
simulation of the evolution of open quantum systems~\cite{Garcia, Wang,Weimer}
and specifically for quantum channels~\cite{Xin,Wei,Zanetti}, 
which can be used to study and model decoherence.
Such quantum algorithms can be represented using what is known as a quantum
circuit~\cite{chuangbook}, which we will study in section \ref{sec: Circuit for a Pauli Channel}.

@@

@@

\tbnote{
Continuing with this previous work done to simulate quantum processes, in this article we 
propose a quantum algorithm for simulating Pauli channels
and implement it on one of IBM's quantum computers.
The algorithm proposed is straightforward and can be used for any Pauli channel by only changing a couple of 
parameters in the operations it performs. 
To represent the algorithm, we use a quantum circuit, which is a common
way of representing algorithms intended for quantum computers.~\cite{chuangbook}.  }

\tbnote{ Furthermore, we will also simulate Pauli dynamical maps, which are continuous parametrized curves of Pauli channels.
These maps can be used to model a continuous change of a qubit instead of only discrete jumps. 
The generality of the algorithm proposed for Pauli channels will be very useful in this part, since then
using for dynamical maps will come very naturally.
Implementing these maps will lead us to study quantum algorithms  with free parameters, 
something that is common in areas such as quantum machine learning~\cite{Benedetti}.
This can be done using parametrized quantum circuits, which consist of quantum
circuits in which one or more operations depend on a free parameter. }

\cpnote{dejar solo un parrafo de estructura:} 
\tbnote{Aqui está:}

We start by providing the definition of quantum channels, the general framework
used here, and multi-qubit Pauli channels in section \ref{sec: Pauli Channels}.
Our first objective is to present a general and straightforward quantum algorithm capable of simulating
Pauli channels on quantum computers; we do this in section \ref{sec: Circuit
for a Pauli Channel}, where we also demonstrate its implementation using IBM's
quantum computers for some single and two-qubit Pauli channels.
Expanding beyond discrete Pauli channels, we introduce the concept of Pauli
dynamical maps, defined as a continuous parametrization of multi-qubit Pauli
channels.  Therefore, in section \ref{sec: 1PR Circuits} we shift our focus to
study parametrized quantum channels, aiming to adapt the algorithm developed
for channels to dynamical maps.  Furthermore, we contribute to the body of work
related to parametrized quantum circuits by establishing a theorem, which  sets
the mathematical conditions for the transformations that can be done using a
parametrized circuit with the restriction that only a controlled single-qubit
rotation in the circuit may depend on the parameter.  Finally, in section
\ref{sec: 1PR circuit for a Pauli map}, we conclude analyzing the Pauli
dynamical maps that fulfill the conditions of theorem \ref{theorem2}.

%
%We start the article by providing the definition of quantum channels, the
%general framework used here, and multi-qubit Pauli channels in section
%\ref{sec: Pauli Channels}.  Then, since our main objective is to obtain a
%parametrized circuit for Pauli dynamical maps, we will first need a circuit
%that can implement any Pauli channel by only changing some parameters in the
%quantum gates and without changing the design of the circuit itself.
%Therefore, in section\ref{sec: Circuit for a Pauli Channel} we present such a
%circuit and we also show its implementation using IBM's quantum computers for
%the particular case of single-qubit Pauli channels and some two-qubit ones.  In
%section \ref{sec: 1PR Circuits}, we adapt the algorithm to dynamical maps.
%Then we aim to simplify the algorithm so that it only contains one parametrized
%single-qubit rotation, and in the process we contribute to the work in
%parametrized quantum circuits by establishing   in \ref{theorem2} which general
%quantum transformations can be implemented this way.  Finally, in section
%\ref{sec: 1PR circuit for a Pauli map}, we conclude analyzing the Pauli
%dynamical maps that fulfill the conditions of theorem \ref{theorem2}.

@@

We can also see how an arbitrary Pauli channel acts on an arbitrary  
density matrix.
To do it, we substitute \eref{eq: Density Matrix} 
in \eref{eq: Pauli channel 1 qbit}:
\begin{equation}
\mathcal{E}(\rho) = \dfrac{1}{2}\sum_{\gamma,\alpha=0}^3 k_{\gamma} r_{\alpha} \sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma}.
\label{eq:Edepol}
\end{equation}
This can be simplified noting that 
\begin{equation}
\sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma} = A_{\alpha,\gamma} \sigma_{\alpha}, \;\;\;\;\; \text{with} \; A = \begin{pmatrix}
1 & 1 & 1 & 1\\
1 & 1 & -1 &-1 \\
1 & -1 & 1 & -1 \\
1 & -1 & -1 & 1
\end{pmatrix},
\label{eq: propiedad-pauli}
\end{equation}
which was obtained following the 
commutation relation of Pauli matrices $[\sigma_\alpha,\sigma_\beta] = 2 i
\epsilon_{\alpha \beta \gamma} \sigma_\gamma$ and $\epsilon_{\alpha \beta \gamma}$ is 
the Levi-Civita tensor. Then, \eref{eq:Edepol} takes the form
% 
% 
% 
% 
% This can be simplified by using the following property of Pauli matrices:
% \revnote{Really confusing notation, I suggest use the much more well known relation using the Levi-Civita tensor.}
% 
% 
% \tbnote{Siguiendo la relaci\'on de conmutaci\'on, resulta que las Levi Civitas desaparecen y quedan s\'olo deltas de Dirac:}
% {\color{green}
% \begin{equation*}
% \sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma}  =   A_{\alpha,\gamma} \sigma_{\alpha}, \;\;\;\;\;\; \text{with} \; A_{\alpha, \gamma} = (2\delta_{ij}-1)(2\delta_{i0}-1)(2\delta_{j0}-1)
% \end{equation*}
% }
% 
% 
% \begin{equation}
% \label{eq: propiedad-pauli}
% \sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma} = A_{\alpha,\gamma} \sigma_{\alpha}, \;\;\;\;\; \text{with} \; A = \begin{pmatrix}
% 1 & 1 & 1 & 1\\
% 1 & 1 & -1 &-1 \\
% 1 & -1 & 1 & -1 \\
% 1 & -1 & -1 & 1
% \end{pmatrix},
% \end{equation}
% which leads to
\begin{equation}
\label{eq: rho-transformada}
\mathcal{E}(\rho) = \dfrac{1}{2} \sum_{\alpha} \left(\sum_{\gamma} A_{\alpha, \gamma} k_{\gamma} \right) r_{\alpha} \sigma_{\alpha}.
\end{equation}
\eref{eq: rho-transformada} once again has the form of \eref{eq: Density Matrix}
but with components $\left( \sum_{\gamma} A_{\alpha,\gamma} k_{\gamma} \right) r_{\alpha}$.
This gives us another way of understanding Pauli channels
as operations that take each component $r_{\alpha}$
of the density matrix and multiplies them
by $\sum_{\gamma} A_{\alpha,\gamma} k_{\gamma}$, 
that is:
\begin{equation}
\label{eq: multipliers}
r_{\alpha}  \xrightarrow[\text{Channel}]{\text{Pauli}}  \tau_{\alpha} r_{\alpha} ,\;\; \tau_{\alpha} := \sum_{\gamma} A_{\alpha,\gamma} k_{\gamma}.
\end{equation}
Notice that $\tau_0 = 1$, which is a consequence of $\sum_{\gamma}k_{\gamma}=1$
and ensures that after the channel, the resulting density matrix still has trace one. 
Furthermore, reverting the definition of $\tau_{\alpha}$ by using that $A^{-1} = \dfrac{1}{4} A$, 
we get that $k_{\gamma} = \dfrac{1}{4} \sum_{\alpha} A_{\alpha,\gamma} \tau_{\alpha}$.
Then, using that $k_{\gamma} \geq 0$
we get the following conditions on the multipliers $\tau_{\alpha}$:
\begin{eqnarray}
\label{eq: conditions-tetrahedron}
&1+\tau_i -\tau_j - \tau_k \geq 0,  \;\;\; \text{for $i,j,k$ different numbers in $\{1,2,3\}$}, \\
&1+\tau_1 + \tau_2 + \tau_3 \geq 0.
\end{eqnarray}

@@

{\color{green}
\subsection{Simulation of a two-qubit Pauli channel}

For the case of a two-qubit Pauli channel,
the circuit of \fref{Fig1} would have two main
qubits and four ancilla qubits, on which it would be necessary to create the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma}\rangle$.
However, since the quantum computer ibmq-lima we used does not have that many qubits,
we will simulate a Pauli channel that does not apply all two-qubit Pauli matrices to the system.
For example, consider the following two-qubit dephasing channel:
\begin{align}
\varepsilon (\rho) = (1-p) \rho + \dfrac{p}{3} (I \otimes \sigma_z) \rho (I \otimes \sigma_z) +  \dfrac{p}{3}(\sigma_z \otimes I) \rho (\sigma_z \otimes I) +  \dfrac{p}{3}(\sigma_z \otimes \sigma_z) \rho (\sigma_z \otimes \sigma_z),
\label{2qbit-c}
\end{align}
where $p \in [0,1]$ is a parameter that defines the channel. 
Since this channel has $4$ Pauli operations, 
only $2$ ancilla qubits will be necessary, and it can be implemented
using the circuit of \fref{2qbit}b.
